<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Getting started with the 'mh' package}
-->

=================

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"', fig.align="center", fig.width=10, fig.height=8, dev='png')
```

# About this document

This document was generated from an R markdown file on `r as.character(Sys.time())`. It illustrates how to set up a calibration on a time stepping model simulation.

```{r, eval=FALSE, include=FALSE}
library(swiftdev)
setwd(file.path('F:/src/github_jm/metaheuristics/R/pkgs/mh', 'vignettes'))
purlVignettes('.', '..')
```

# Getting started

```{r}
library(mh)
```

The package includes a simplified but realistic example of a system to optimize, a time stepping simulation model written in C#. We can load the modelling system, and an assembly that provides adapters so that this system can be calibrated.

```{r}
mhDllDir <- system.file(package='mh', 'libs')
fnSampleEnv <- file.path(mhDllDir, "EnvModellingSample.dll" )
fnAdapter <- file.path(mhDllDir, "ModellingSampleAdapter.dll" )
stopifnot(file.exists(fnSampleEnv))
stopifnot(file.exists(fnAdapter))
clrLoadAssembly(fnSampleEnv)
clrLoadAssembly(fnAdapter)

clrGetTypesInAssembly("ModellingSampleAdapter")
clrGetStaticMethods("ModellingSampleAdapter.OptimizationAdapter")
```

We configure the sample modelling system, an implementation of the Australian Water Balance Model and a simulation shell that relies on very simple arrays for input/outputs and 'time' stepping. We will calibrate the model against runoff observations, so we set it up to record the 'Runoff' output.

```{r}
simul <- clrCallStatic("EnvModellingSample.SimulationFactory", "CreateAwbmSimulation", TRUE)
simul
clrCall(simul, 'Record', 'Runoff')
```

The assembly with the adapters provides a method to get a default feasible parameter space for this AWBM model

```{r}
p <- clrCallStatic("ModellingSampleAdapter.OptimizationAdapter", "BuildParameterSpace", simul)
p
pSetAsDataFrame(p)
```

The default bounds are large; for this model we usually expect the KSurf parameter to be rather below 0.5 (meaning its reservoir is emptying fast, being a surface store). Let's illustrate how to set other feasible bounds. We can discover the members of the .NET object interactively:

```{r}
clrReflect(p)
clrGetMemberSignature(p, 'SetMaxValue')
clrCall(p, 'SetMaxValue', 'KSurf', 0.5)
```

Now let's define the objective; the sample only provides for least squares as an objective function ('ss').

```{r}
observation <- clrCallStatic("EnvModellingSample.DataHandling", "GetSampleRunoff")
observation[observation < 0] <- NA
plot(observation, type='l')

from <- clrCall(simul, 'GetStart') + 365L
to <- clrCall(simul, 'GetEnd')

objective <- clrCallStatic("ModellingSampleAdapter.OptimizationAdapter", "BuildEvaluator", simul, observation, from, to, "ss")

score <- getScore(objective, p)
score
```

Now let's move on to the optimizer. We define a few functions to condensate the syntax; you need not look closely to the following function definitions in the first instance to get the 'gist of it'

```{r}
createSceOptimHelper <- function(objective, parameterizer, sysConfigType = NULL, terminationCriterion = NULL) {
  if(is.null(sysConfigType))  sysConfigType <- hyperCubeType()
  if(is.null(terminationCriterion)) terminationCriterion <- maxWallTimeTermination(sysConfigType)
  createSceOptim(objective, parameterizer, sysConfigType, terminationCriterion)
}

getMarginalTermination <- function(tolerance = 1e-06, cutoffNoImprovement = 10, maxHours = 0.05, sysConfigType=NULL) {
  if(is.null(sysConfigType))  sysConfigType <- hyperCubeType()
  mh::marginalImprovementTermination(sysConfigType, tolerance = tolerance, cutoffNoImprovement = cutoffNoImprovement, maxHours = maxHours) 
}

setCalibrationLogger <- function (optimizer) 
{
    calibLogger <- clrNew("CSIRO.Metaheuristics.Logging.InMemoryLogger")
    clrSet(optimizer, "Logger", calibLogger)
}
```

Now let's move ou to the optimizer. We define a few functions to condensate the syntax; you need not look closely to the following functions in the first instance to get the 'gist of it'

```{r}
optimizer <- createSceOptimHelper(objective, p, terminationCriterion = getMarginalTermination())
calibLogger <- setCalibrationLogger(optimizer)
```

The default optimiser is set such that if the model is thread safe (and the sample we use is indeed), parallel computing is used, and happens to default to 5 parallel threads. If you wish a lower limit, e.g. if you have a 4 core machine, you may limit this to e.g. 3 cores with the command:

```{r}
# clrSet(optimizer, "MaxDegreeOfParallelism", 3L)
```

Let's "solve" the optimisation problem now fully defined:

```{r}
library(lubridate)
startTime <- now()
calibResults <- clrCall(optimizer, "Evolve")
endTime <- now()
calibWallTime <- endTime-startTime
print(paste( 'Optimization completed in ', calibWallTime, attr(calibWallTime, 'units')))
```

We set up a calibration logger so that we have access to more details to assess how the optimizer performed and behaved.

```{r}
logMh <- mh::processLogger(optimizer, fitness='Sum.Squares')  # TODO: illustrate where this name for the fitness comes from...
geomOps <- mh::subsetByMessage(logMh)
str(geomOps@data)
```

We can then visualize how the calibration evolved. There are many types of visualisations included in the **mh** package, and numerous customizations possible, but starting with the overall population evolution:

```{r}
pVarIds <- (pSetAsDataFrame(p))$Name
for (pVarId in pVarIds) {
	print(plotParamEvolution(geomOps, pVarId))
}
```

The results of an SCE calibration is a population of points, albeit one with a best point in this case (single objective calibration). Accessing it is possible in a couple of ways (and TODO: improve access arrangements...).

```{r}
clrReflect(calibResults)
scores <- clrGet(calibResults,  "ObjectiveScores" )
is.list(scores)
score <- scores[[length(scores)]]
clrReflect(score)
clrGet(score, "SystemConfiguration")
pSetAsDataFrame( clrGet(score, "SystemConfiguration"))
```

Another way to access calibration results is to look at the log:

```{r}
tail(logMh@data)
```
